Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-06 paperICSME.tex
Escribiendo las referencias que los revisores nos dijeron en related work

\begin{itemize}
  \item bug seeding studies, e.g., \textit{``This earlier change is the one that caused the later fixed''}~\cite{williams2008szz} or \textit{``The lines affected in the process of fixing a bug are the same one that originated or seeded that bug''}~\cite{izquierdo2011developers},
  \item bug fix patterns, e.g., \textit{``The version before the bug fix revision is the bug version''}~\cite{pan2009toward},
  \item tools that prevent future bugs, e.g., \textit{``We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit''}~\cite{fejzer2015supporting}. 
\end{itemize}

@@

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 463 times as of January 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations. Hence, there is a myriad of articles that use SZZ on an ample number of scenarios. Without trying to be exhaustive, we offer several examples. Therefore, Yang et al. apply SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}. Zimmermann et al. use it for predicting bugs in large software systems~\cite{zimmermann2007predicting}. Kim et al. show how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. Kamei et al. apply it to validate effort-aware bug-prediction models~\cite{kamei2010revisiting}. Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}. Izquierdo et al. use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}. Yin et al. use SZZ to find how many fixes to bugs introduce new bugs~\cite{yin2011fixes}. Tantithamthavorn et al. employ it to quickly identify the location of a bug~\cite{tantithamthavorn2013mining}. Fejzer et al. use it to support code review~\cite{fejzer2015supporting}. Asaduzzaman et al. apply the SZZ algorithm on Android to study its maintainability~\cite{asaduzzaman2012bug}.

%Bachmann et al. on the missing link between comments in change logs and bug fixes ~\cite{bachmann2010missing}
%Wu et al. propose a tool solution~\cite{wu2011relink}

%\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}. There the talk is precisely about those bugs whose origina are elsewhere. Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}

@@

@@

On the other hand, the question of whether a bug report is really a bug or not has been widely studied in the 
mining software repositories research literature in the last years. Therefore, Pan et al. classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}. Antoniol et al. have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}. Herzig et al. have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sense that they were not a bug report but a feature request, an internal refactoring or an update to documentation~\cite{herzig2013s}. They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools.

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

>>>>

\begin{itemize}
  \item bug seeding studies, e.g., \textit{``This earlier change is the one that caused the later fixed''}~\cite{williams2008szz} or \textit{``The lines affected in the process of fixing a bug are the same one that originated or seeded that bug''}~\cite{izquierdo2011developers},
  \item bug fix patterns, e.g., \textit{``The version before the bug fix revision is the bug version''}~\cite{pan2009toward},
  \item defect prediction studies,  e.g., \textit{``A line that is deleted or changed by a bug-fixing change is a faulty line''}~\cite{altman1968financial},
  \item tools that prevent future bugs, e.g., \textit{``We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit''}~\cite{fejzer2015supporting}. 
\end{itemize}

@@

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 475 times as of April 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations. Hence, there is a myriad of articles that use SZZ on an ample number of scenarios. Without trying to be exhaustive, we offer several examples. Therefore, Yang et al. apply SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}. Zimmermann et al. use it for predicting bugs in large software systems~\cite{zimmermann2007predicting}. Kim et al. show how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. Kamei et al. apply it to validate effort-aware bug-prediction models~\cite{kamei2010revisiting}. Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}. Izquierdo et al. use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}. Yin et al. use SZZ to find how many fixes to bugs introduce new bugs~\cite{yin2011fixes}. Tantithamthavorn et al. employ it to quickly identify the location of a bug~\cite{tantithamthavorn2013mining}. Fejzer et al. use it to support code review~\cite{fejzer2015supporting}. Altman et al. use it to predict whether a change is buggy at the time of a commit, evaluating the change classification techniques to address the incorrect evaluation presented by cross-validation ~\cite{altman1968financial}. Asaduzzaman et al. apply the SZZ algorithm on Android to study its maintainability~\cite{asaduzzaman2012bug}.

%\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}. There the talk is precisely about those bugs whose origina are elsewhere. Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}

@@

Kamei et al. used the 'Just-in Time Quality Assurance' concept, which focuses in identifying defect-prone at level of software changes/patches instead of files or packages. Allowing developers can review these risky changes while they are still fresh in their minds. In the paper, they present a change risk model in which several characteristics of a software changes are implemented(lines added, developer experience...). They empirically evaluated their approach to identify in real time software changes that would be a defect ~\cite{kamei2013large}. Altman et al. used the same concept to carried out a study where the authors applied change classification on a proprietary code case, sharing the experience and lesson learned. They concluded that interpretable prediction models are needed for software defect prediction~\cite{altman1968financial}.

@@

On the other hand, the question of whether a bug report is really a bug or not has been widely studied in the 
mining software repositories research literature in the last years. Therefore, Pan et al. classify the different types of bug-fix patterns that most commonly exist~\cite{pan2009toward}. Antoniol et al. have use a text-based approach to classify bug reports into corrective maintenance and other kinds of activities~\cite{antoniol2008bug}. Herzig et al. have done a manual examination of thousands of bug reports and have found that around a third of them are misclassified, in the sense that they were not a bug report but a feature request, an internal refactoring or an update to documentation~\cite{herzig2013s}. They show that almost 40\% of the files marked as defective did not have a bug, and suggest that this missclassification introduces bias in bug prediction models and tools. Tantithamthavorn et al. investigated the nature of mislabelled issue reports and how this mislabelled impact in the prediction models, achieving that the mislabelling presented in the issue reports is not random. Furthermore, after training models with clean and noise data, they obtained the same accuracy in the results~\cite{tantithamthavorn2015impact}.

%\gema{A brief summary about "A Large-Scale Empirical Study of Just-in-Time Quality Assurance": In this paper the concept of 'Just-in Time Quality Assurance' is presented, this concept focus in identifying defect-prone at level of software changes/patches instead of files or packages, this way the developers can review these risky changes while they are still fresh in their minds. In the paper they present as change risk model in which several characteristics of a software changes are implemented(lines added, developer experience...) They want provide an effort-reducing way to focus on the most risky changes, they empirically evaluated their approach in "Just-In-Time Quality Assurance" to identify in real time software changes that would be a defect}

%\gema{A brief summary about "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models", \cite{tantithamthavorn2015impact}: In the paper the authors carried out a study where investigated the nature of mislabelled issue reports and also how this mislabelled impact in the prediction models. Finding that the mislabelling is not random. Furthermore the models trained using data noise are often just as accurate as the ones trained with clear data, but using clear data will likely allow the models to identify more of the truly defective modules. }

%\gema{A brief summary about "Online Defect Prediction for Imbalanced Data",\cite{altman1968financial}: A change classification can predict whether a change is buggy at the time of the commit, which allow to developers to act on the prediction results as soon as a commit is made, the benefit is that reviewers have less code to examine to identify defect, but the problem is that for the same reason is more difficult to predict on changes accurately. The authors applied change classification on a proprietary code case and share the experience and lesson learned. They evaluated the change classification techniques to address the incorrect evaluation presented by cross-validation, and applied some techniques improving the precision, they conclude that interpretable prediction models  are needed for software defect prediction, They used the SZZ approach saying that 'A line that is deleted or changed by a bug-fixing change is a faulty line'}
